Krill EMC Results - ICES J. Marine Science - resubmission
South Georgia example
September 2017

========================================================

Results for the South Georgia example providing the specific graphics
for resubmission.

```{r,echo=FALSE}
## plot for publication

PLOT.TIF <- TRUE  # make TRUE (not FALSE) if wishing to plot to TIF file

```

```{r}
# 0. Set up directories, functions, libraries and initial parameters for test

# 0.1 ancillary directories

dir_fns<-"Fns\\"
dir_data<-"Data\\"
dir_out<-"Out\\"

# 0.2 load functions 

# old source(paste(dir_fns,"Growth_Fn_EMC.r",sep=""))

source(paste(dir_fns,"Growth_Fn_EMC_v2.r",sep=""))
source(paste(dir_data,"Growth_data_KrillParams.r",sep=""))
source(paste(dir_data,"Growth_data_KrillSizeAtAge.r",sep=""))

# 0.3 load libraries

library(plotrix)
library(R2HTML)

# 0.4. initialise parameters (EMC_p)

source(paste(dir_data,"Growth_data_KrillParams.r",sep=""))

# 0.5. Area-specific environment (AreaEnv) and other local variables

source(paste(dir_data,"Growth_data_Env.r",sep=""))

```

# 1. Initialise conditions for parsing to the function and name according to function variables

```{r}
# 1.1 Initialise trial

ActiveArea<-20  # which area is to be used
                # note that this will be made into a relative abundance of food

Start_asPropYr <- 0  # 1 January
Gstate<-list(iG     = 0 # investment in growth within moult
            ,IMP    = 0 # where IMP is prop of IMP completed
            ,IMPtime = 0 # time in IMP so far (years)
            ,DayLength_LastMoult = DL_EMC(Area_lat[Area_n==ActiveArea],Start_asPropYr)  # day length at last moult
            )

Rstate<-list(iR     = 0 #   Ir is investment in reproduction within moult cycle
           , Moults = 0 # how many moults have passed in stage of cycle
           , Cycle  = 3 # which stage of the cycle is currently active  - note that this is set for any age
           )

Carbon<-list(Cingest = 0
            ,Cassim  = 0
            ,Cegest  = 0
            ,Cexcess = 0
            ,BodyCarbon = NA
            )
Local<-list(AreaLat = Area_lat[Area_n==ActiveArea]  # latitude of location to give day length
            , Env = AreaEnv[(AreaEnv[,1]==ActiveArea),c(3:ncol(AreaEnv))]
            )


```


# Population for weighting food available for each age class

convert time series of carbon for area relative to individual krill 
by setting up a population and its consumption for a time interval


```{r}

##################
# set weighted availability of food for each age class based on deterministic model

TwoSex<-TRUE
Nsex<-2
SexRatio<-c(0.5,0.5)

Ages_N<-6   # note - no more than 8 age classes as per length of CingestPerIMP
Age1<-1
MaxAge<-(Age1+Ages_N-1)
Ages<-c(Age1:MaxAge)
NatMort<-c(0.8,0.8)
  N_age      <- NULL
  L_at_age_vB<- NULL
  WW_at_age  <- NULL
  DW_at_age  <- NULL
  FR_at_age  <- NULL

for(s in 1:Nsex){
  tN_age      <- SexRatio[s]*exp((-NatMort[s])*Ages)
  tN_age[Ages]<- tN_age[Ages]*(1+1/(exp(NatMort[s])-1)) # plus class
  N_age       <- cbind(N_age,tN_age)
  L_at_age_vB <- cbind(L_at_age_vB,Growth.VB(list(Linf=60, K=0.45, T0=0),Ages,0,0))
  WW_at_age   <- cbind(WW_at_age,WW_from_Length(L_at_age_vB[,s],EMC_p$LW,s))
  DW_at_age   <- cbind(DW_at_age,DW_from_Length(L_at_age_vB[,s],EMC_p$LW,s))
  }

N_age     <- N_age/sum(N_age)
FR_at_age <- Fcf_EMC(DW_at_age) # filtration at age (m3.yr-1)


# food becomes limiting when the maximum ingestion rate is not achieved
# thus, the sum of (maximum ingestion rate at age by the frequency at age) can be divided into max food available during a period to give the number in the population 
# that would cause the population to be food limited.

# Local$Env[,1] # proportion of year
# Local$Env[,3] # carbon mg/m2 consumed over the course of the time interval (proportion of year)

# calculate max food consumed for an IMP

# approximate maxima from model runs for SG time series
CingestPerIMP<-c(75,283,592,931,1334,1802,2332,2928) #mg per IMP (0.04*365)
CingestPerIMP<-CingestPerIMP[c(1:Ages_N)]    # note - no more than 8 age classes as per length of CingestPerIMP
CingestPerDay<-CingestPerIMP/(0.04*365)
if(TwoSex) CingestPerDay<-cbind(CingestPerDay,CingestPerDay)
Ntotal<-max(Local$Env[,3]/Local$Env[,1])/365/sum(N_age*CingestPerDay) 

Depth <- Ntotal*sum(N_age*FR_at_age)/43080448642/365 # volume m-2 day-1

print(paste("Total N at SG = ",Ntotal,sep=""))
print(paste("Total B at SG = ",(Ntotal*sum(WW_at_age*N_age))*(1E-9),sep=""))
print(paste("Depth   = ",Depth,sep=""))

# Scale the filtering efficiency according to competition coefficients and the food
# available per volume (same units as filtering rate)
# 
# Filtering Efficiency is used to scale the food in the area to available food per volume for an individual

AreaVol<-43080448642 * Depth
Local$Env[,3]<-Local$Env[,3]/AreaVol *Local$Env[,1] # convert to mgC.m-3 for the time period

Filt_Eff<- 0.063  # set this to determine how much of the food is available in the volume being filtered (accounts for competition)
  
print(Local$Env)
```




## 2.3 Loop through 8 years (start with only one year)

```{r}
# compare with 2 g.cm-3 average annual mean

t1<-sum(Local$Env[,3]/365)/sum(Local$Env[,1])
print(t1)
print(2E-3/t1)
```



```{r}
# Set specific conditions for trial

Start.Age<-1
Start.Length<-20   
Start.WhichSex<-2   # 1 = male, 2 = female, 3 = mature female
Start.StartProj<-0  # project for one year
Start.EndProj<-1

ResMoults<-NULL
for (s in 1:Nsex){
Run.WhichSex<-if(Nsex==1) Start.WhichSex else s

Age    <- Start.Age
Length <- Start.Length
DryWeight<-DW_from_Length(Length,EMC_p$LW,Run.WhichSex)
Kstate<-list(Gro=Gstate, Rep = Rstate, Carbon = Carbon, Female= (if(Run.WhichSex==1) FALSE else TRUE))
Kstate$Carbon$BodyCarbon<-CW_from_Length(Length,EMC_p$LW,2)
StartProj<-Start.StartProj  # project for one year
EndProj<-Start.EndProj

ResMoults<-rbind(ResMoults,
                 c(0,Age,(if(Run.WhichSex==1) 1 else  
                   2),0,0,0,0,0,0,Length,DryWeight,0,1,Age,0))
Total_proj<-NULL

for (i in 1:Ages_N){
res<-Growth_EMC(Age      
          ,Length     
          ,DryWeight
          ,Kstate
          ,Filt_Eff
          ,StartProj   
          ,EndProj     
          ,Local       
          ,EMC_p       
          )
Age  <-  res$Age
Length  <- res$Length   
DryWeight <-res$DryWeight
Kstate        <- res$Kstate      
Total_proj<-res$Total
ResMoults<-rbind(ResMoults,matrix(res$Moults$Data,ncol=res$Moults$Vars,byrow=res$Moults$ByRow))
} # end age
} # end sex

# Results for each moult are in res$Moults
 
dimnames(ResMoults)[[2]]= c("Moult"
                            ,"Age"
                            ,"Sex"
                            ,"IMPtime"
                            ,"Ration"
                            ,"Cingest"
                            ,"Cmet"
                            ,"Cegest"
                            ,"Carbon_ThisMoult"
                            ,"Length"
                            ,"DryWeight"
                            ,"GonadDW"    # >0 even if no eggs when only first moult, or insufficient to reproduce
                            ,"StCond"
                            ,"AgeReprod"
                            ,"Eggs")

print(ResMoults[c(1:20),])

# print(cbind(ResMoults[,"Age"],ResMoults[,"Cingest"],(ResMoults[,"Cingest"]-ResMoults[,"Cegest"])))
```


###Plot time series data


```{r, echo=FALSE}



# Plot for publication

# Extract data for plotting
PD<-ResMoults[,c("Age","Sex","Length","DryWeight","Eggs")]

PD_male<-PD[PD[,2]==1,]
PD_female<-PD[PD[,2]==2,]


plot.WhichSex<-if(TwoSex) 1 else Start.WhichSex

############# Graphics ready for printing to TIF file
#if(PLOT.TIF) tiff(filename = "EMC_Environment.tif", width = 1500, height = 960, units = "px", pointsize = 24)

if(PLOT.TIF) tiff(filename = "EMC_time_series_SG v1.tif", width = 170, height = 100, units = "mm", res=300)

par(mar=c(3, 12, 2, 4) + 0.1) # as much space in left margin as possible
par(cex.axis=0.75)

xAge<-PD[,'Age']
Xlim_Age<-c(Age1,(MaxAge+1))
Xlab<-"Age (Years)"

Ylim_Len<-c(0,65)
col_Len<-"black"
lty_Len<-c(6,3,1)  # males, females, mean
lwd_Len<-c(1,1,1.5) # males, females, mean
Ylab_Len<-'Length (mm)'

Ylim_DW<-c(0,550)
col_DW<-"blue"
lty_DW<-c(6,3,1)  # males, females, mean
lwd_DW<-c(1,1,1.5) # males, females, mean
Ylab_DW<-'Body Dry Weight (mg)'

Ylim_Eggs<-c(0,9000)
col_Eggs<-"red3"
pch_Eggs<-20
lwd_Eggs<-1
Ylab_Eggs<-'Eggs'

# length

plot(PD[PD[,"Sex"]==plot.WhichSex,"Age"],PD[PD[,"Sex"]==plot.WhichSex,"Length"],axes=F, xlab="",ylab=""
        ,xlim=Xlim_Age,ylim=Ylim_Len,type="l",col=col_Len
        ,lty=lty_Len[plot.WhichSex], lwd=lwd_Len[plot.WhichSex])
if(TwoSex) {
  lines(PD[PD[,"Sex"]==2,"Age"],PD[PD[,"Sex"]==2,"Length"],col=col_Len,lty=lty_Len[2],lwd=lwd_Len[2])
  lines(PD_male[,"Age"],((PD_male[,"Length"]+PD_female[,"Length"])/2),col=col_Len,lty=lty_Len[3],lwd=lwd_Len[3])  # mean size at age
  }
# plot vB for comparison
xInt<-10
xAges<-c((Age1*xInt):((MaxAge+1)*xInt))/xInt
yVB<-Growth.VB(SizeAtAge_p$VB,xAges,0,0)
lines(xAges,yVB,col="black",lwd=1,lty=1)  # plot vB for comparison



axis(2, ylim=Ylim_Len,col=col_Len,lwd=1,col.axis=col_Len)
mtext(2,text=Ylab_Len,line=2,col=col_Len, cex=0.75)

par(new=T)
plot(PD[PD[,"Sex"]==plot.WhichSex,"Age"],PD[PD[,"Sex"]==plot.WhichSex,"DryWeight"],axes=F, xlab="",ylab=""
        ,xlim=Xlim_Age,ylim=Ylim_DW,type="l",col=col_DW
        ,lty=lty_DW[plot.WhichSex], lwd=lwd_DW[plot.WhichSex])
if(TwoSex) {
  lines(PD[PD[,"Sex"]==2,"Age"],PD[PD[,"Sex"]==2,"DryWeight"],col=col_DW,lty=lty_DW[2],lwd=lwd_DW[2])
  }

axis(2, ylim=Ylim_DW,lwd=1,line=3.5, col=col_DW,col.axis=col_DW)
mtext(2,text=Ylab_DW,line=5.5, col=col_DW, cex=0.75)

par(new=T)
plot.WhichSex<-2
#xD<-PD[(PD[,"Sex"]==plot.WhichSex & PD[,"Eggs"]>0),"Age"]
#yD<-PD[(PD[,"Sex"]==plot.WhichSex & PD[,"Eggs"]>0),"Eggs"]
#plot(xD,yD,axes=F, xlab="",ylab="",xlim=Xlim_Age,ylim=Ylim_Eggs,type='p',pch=pch_Eggs, col=col_Eggs)

xD<-PD[(PD[,"Sex"]==plot.WhichSex),"Age"]
yD<-PD[(PD[,"Sex"]==plot.WhichSex),"Eggs"]
plot(xD,yD,axes=F, xlab="",ylab="",xlim=Xlim_Age,ylim=Ylim_Eggs,type='l',lwd=lwd_Eggs, col=col_Eggs,lty=1)

axis(2, ylim=Ylim_Eggs,lwd=1,line=7, col=col_Eggs,col.axis=col_Eggs)
mtext(2,text=Ylab_Eggs,line=9, col=col_Eggs, cex=0.75)


#We can now draw the X-axis, which is of course shared by all the three time-series.

axis(1,pretty(range(1,8),10))
mtext(Xlab,side=1,col='black',line=2, cex=0.75)


# return plotting to terminal

if(PLOT.TIF) dev.off()

############# End printing to TIF file


```




###Plot example annual growth and reproductive cycle for example age

Data for plotting

```{r, echo=FALSE}

# plot info

egAGE<-5

Xlim<-c(0,1)
Xlab<-"Proportion of Calendar Year"

# Extract data for plotting - reproductive female to demonstrate investment in body and gonads, coupled with shrinking

PD1<-ResMoults[(ResMoults[,"Sex"]== 2),]
FirstRow<-nrow(PD1[(PD1[,"Age"]< egAGE),])
LastRow<-nrow(PD1[(PD1[,"Age"]< (egAGE+1)),])+1
PD<-PD1[c(FirstRow:LastRow),]

# c("Moult","Age","Sex","IMPtime","Ration","Cingest","Cmet","Cegest","Carbon_ThisMoult","Length","DryWeight","GonadDW","StCond","AgeReprod","Eggs")

# adjust the first row to be time 0 in the year
PD_0<-PD[1,]

if(PD_0['Age']!=egAGE){
PD_0['Age']<-egAGE
PD_0['IMPtime']<-NA
PD_0['Ration']<-PD[2,'Ration']*(egAGE-PD[1,'Age'])/(PD[2,'Age']-PD[1,'Age'])
PD_0['Cingest']<-PD[2,'Cingest']*(egAGE-PD[1,'Age'])/(PD[2,'Age']-PD[1,'Age'])
PD_0['Cmet']<-PD[2,'Cmet']*(egAGE-PD[1,'Age'])/(PD[2,'Age']-PD[1,'Age'])
PD_0['Cegest']<-PD[2,'Cegest']*(egAGE-PD[1,'Age'])/(PD[2,'Age']-PD[1,'Age'])
PD_0['Carbon_ThisMoult']<-NA
PD_0['DryWeight']<-PD_0['DryWeight']+(PD[2,'DryWeight']-PD[1,'DryWeight'])*(egAGE-PD[1,'Age'])/(PD[2,'Age']-PD[1,'Age'])
PD_0['GonadDW']<-{
        if(PD_0['Eggs']>0) PD[2,'GonadDW']*(egAGE-PD[1,'Age'])/(PD[2,'Age']-PD[1,'Age']) else
          PD_0['GonadDW']+(PD[2,'GonadDW']-PD[1,'GonadDW'])*(egAGE-PD[1,'Age'])/(PD[2,'Age']-PD[1,'Age'])
}
PD_0['AgeReprod']<-NA
PD_0['Eggs']<-NA
PD[1,]<-PD_0
} # end if Age


# adjust the last row to be time 1 in the year
nR<-nrow(PD)
nRp<-nR-1

aL<-egAGE+1
PD_L<-PD[nR,]

if(PD_L['Age']!=(egAGE+1)){
PD_L['Age']<-aL
PD_L['IMPtime']<-NA
PD_L['Ration']<-PD[nR,'Ration']  *(aL-PD[nRp,'Age'])/(PD[nR,'Age']-PD[nRp,'Age'])
PD_L['Cingest']<-PD[nR,'Cingest']*(aL-PD[nRp,'Age'])/(PD[nR,'Age']-PD[nRp,'Age'])
PD_L['Cmet']<-PD[nR,'Cmet']      *(aL-PD[nRp,'Age'])/(PD[nR,'Age']-PD[nRp,'Age'])
PD_L['Cegest']<-PD[nR,'Cegest']  *(aL-PD[nRp,'Age'])/(PD[nR,'Age']-PD[nRp,'Age'])
PD_L['Carbon_ThisMoult']<-NA
PD_L['DryWeight']<-PD[nRp,'DryWeight']+(PD[nR,'DryWeight']-PD[nRp,'DryWeight'])*(aL-PD[nRp,'Age'])/(PD[nR,'Age']-PD[nRp,'Age'])
PD_L['GonadDW']<-{
        if(PD[nRp,'Eggs']>0) PD[nRp,'GonadDW']*(aL-PD[nRp,'Age'])/(PD[nR,'Age']-PD[nRp,'Age']) else
          PD[nRp,'GonadDW']+(PD[nR,'GonadDW']-PD[nRp,'GonadDW'])*(aL-PD[nRp,'Age'])/(PD[nR,'Age']-PD[nRp,'Age'])
         }
PD_L['AgeReprod']<-NA
PD_L['Eggs']<-NA

PD[nR,]<-PD_L
} # end if age

print(PD)
```

Data for plotting tick marks of each Moult, and gonad dry weight

```{r, echo=FALSE}

# plot IMP intervals on the X-axis
xIMP<-PD[!is.na(PD[,'IMPtime']),'Age']-egAGE
yIMP_base<-4
yIMP_TickLen<-(-0.1)
yIMP_TickGonadMultiplier<-1.5

GonadGT0<-PD[!is.na(PD[,'IMPtime']),'GonadDW']>0

yIMP_Tick<-rep(yIMP_TickLen,length(xIMP))
yIMP_Tick[GonadGT0]<-yIMP_TickGonadMultiplier*yIMP_TickLen
yIMP<-cbind(rep(yIMP_base,length(xIMP)),(yIMP_Tick+yIMP_base))

col_IMP<-rep('black',length(xIMP))
col_IMP[GonadGT0]<-'red3'
lwd_IMP<-1
Ylim_IMP<-c(0,4)
Xlim_IMP<-c(0,1)
plot(NA, NA, axes=F, ylim=Ylim_IMP, xlab='', ylab='', main='', xlim=Xlim_IMP)
for (i in 1:length(xIMP)) lines(rep(xIMP[i],2),yIMP[i,],col=col_IMP[i],lwd=lwd_IMP)

# plot x-axis
axis(1,pretty(range(0,1),10))
mtext(Xlab,side=1,col='black',line=2)


# gonad dry weight matrix - col 1 = time of year, col 2 = gonad dry weight
# shows resetting of gonad to zero after eggs have been spawned
yGDW<-PD[,'GonadDW']
xGDW<-PD[,'Age']-egAGE
xGonadDW<-NULL
yGonadDW<-NULL
whichEggs<-c(0,which(PD[,'Eggs']>0))
for (i in 2:length(whichEggs)){
  xGonadDW<-c(xGonadDW,xGDW[c((whichEggs[(i-1)]+1):whichEggs[i])],xGDW[whichEggs[i]])
  yGonadDW<-c(yGonadDW,yGDW[c((whichEggs[(i-1)]+1):whichEggs[i])],0)
}
# then add the rest of the vectors
  xGonadDW<-c(xGonadDW,xGDW[c((whichEggs[length(whichEggs)]+1):length(xGDW))])
  yGonadDW<-c(yGonadDW,yGDW[c((whichEggs[length(whichEggs)]+1):length(yGDW))])


plot(xGonadDW,yGonadDW,type="l",col="red3")
print(cbind(xGonadDW,yGonadDW))

```


Plot of example (age,sex) over one year

```{r, echo=FALSE}

############# Graphics ready for printing to TIF file

if(PLOT.TIF) tiff(filename = "EMC_example_Age v1.tif", width = 170, height = 100, units = "mm", res=300)

par(mar=c(3, 12, 2, 4) + 0.1) # as much space in left margin as possible
par(cex.axis=0.75)

xTimeOfYear<-PD[,'Age']-egAGE
Xlim<-c(0,1)
Xlab<-"Proportion of Calendar Year"

Ylim_Len<-c(30,50)
col_Len<-"black"
lty_Len<-1
lwd_Len<-1
Ylab_Len<-'Length (mm)'

Ylim_DW<-c(0,250)
col_DW<-"blue"
lty_DW<-3
lwd_DW<-1
Ylab_DW<-'Body Dry Weight (mg)'

Ylim_GonadDW<-c(0,120)
col_GonadDW<-"red3"
lty_GonadDW<-8
lwd_GonadDW<-1
Ylab_GonadDW<-'Gonad Dry Weight (mg)'

# length
plot(xTimeOfYear, PD[,'Length'], axes=F, ylim=Ylim_Len, xlab='', ylab='', type='l', col=col_Len, lty=lty_Len,main='', xlim=Xlim, lwd=lwd_Len)
axis(2, ylim=Ylim_Len,col=col_Len,lwd=1,col.axis=col_Len)
mtext(2,text=Ylab_Len,line=2,col=col_Len,cex=0.75)

par(new=T)
plot(xTimeOfYear, PD[,'DryWeight'], axes=F, ylim=Ylim_DW, xlab='', ylab='', type='l', col=col_DW, lty=lty_DW, main='', xlim=Xlim, lwd=lwd_DW)
axis(2, ylim=Ylim_DW,lwd=1,line=3.5, col=col_DW,col.axis=col_DW)
mtext(2,text=Ylab_DW,line=5.5, col=col_DW,cex=0.75)

par(new=T)
plot(xGonadDW, yGonadDW, axes=F, ylim=Ylim_GonadDW, xlab='', ylab='', type='l', col=col_GonadDW, lty=lty_GonadDW, main='',xlim=Xlim,lwd=lwd_GonadDW)
axis(2, ylim=Ylim_GonadDW,lwd=1,line=7, col=col_GonadDW,col.axis=col_GonadDW)
mtext(2,text=Ylab_GonadDW,line=9, col=col_GonadDW,cex=0.75)

# plot tick marks for IMP & symbols for representing spawning and reproductive phase
par(new=T)
plot(NA, NA, axes=F, ylim=Ylim_IMP, xlab='', ylab='', main='', xlim=Xlim_IMP)
for (i in 1:length(xIMP)) lines(rep(xIMP[i],2),yIMP[i,],col=col_IMP[i],lwd=lwd_IMP)

xSpawnTimes<-xTimeOfYear[whichEggs]
ySpawnTimes<-rep((yIMP_base[1]*(1+0.005)+abs(yIMP_TickLen)),length(xSpawnTimes))
points(xSpawnTimes,ySpawnTimes,pch="s",cex=0.5)

# point for entering gonadal phase
#points(-0.01,ySpawnTimes[1],pch="G",cex=1)
points(xIMP[length(xIMP)],ySpawnTimes[1],pch="G",cex=0.5)

# point for entering regression phase and post-regression phase
points(xTimeOfYear[whichEggs[length(whichEggs)]+4],ySpawnTimes[1],pch="R",cex=0.5)
points(xTimeOfYear[whichEggs[length(whichEggs)]+9],ySpawnTimes[1],pch="P",cex=0.5)

#We can now draw the X-axis, which is of course shared by all the three time-series.

axis(1,pretty(range(0,1),10))
mtext(Xlab,side=1,col='black',line=2,cex=0.75)

# return plotting to terminal

if(PLOT.TIF) dev.off()

############# End printing to TIF file
```





###Plot the Environmental Variables on one graph

```{r, echo=FALSE}
# prepare vectors

nIm<-30  # number of intervals per month
xDayLength<-c(0:100)/100
yDayLength<-DL_EMC(Area_lat[Area_n==ActiveArea],xDayLength)

xTemp<-Local$Env[,'CalPropYrStart']+Local$Env[,'dt']/2
yTemp<-Local$Env[,'Temp']

# now calculate temperature at 0 and 1 in the calendar year
nT<-length(Local$Env[,'dt'])
yT_0<-yTemp[nT]+((1-xTemp[nT])/(1-xTemp[nT]+xTemp[1]))*(yTemp[1]-yTemp[nT])
xTemp<-c(0,xTemp,1)
yTemp<-c(yT_0,yTemp,yT_0)


xF<-Local$Env[,'dt']
yF<-Local$Env[,'Food']

xFi<-NULL
yFood<-NULL
for (i in 1:length(xF)) {
    xFi<-c(xFi,rep(xF[i]/nIm,nIm))
    yFood<-c(yFood,rep(yF[i]/nIm,nIm))
}

xFood<-NULL
for (j in 1:length(xFi)) xFood<-c(xFood,sum(xFi[1:j]))

xFood<-c(0,xFood)
yFood<-c(yFood,yFood[1])



############# Graphics ready for printing to TIF file (set logical above)

if(PLOT.TIF) tiff(filename = "EMC_Environment v1.tif", width = 170, height = 100, units = "mm", res=300)

par(mar=c(3, 12, 2, 4) + 0.1) # as much space in left margin as possible
par(cex.axis=0.75)


Xlim<-c(0,1)
Xlab<-"Proportion of Calendar Year"

Ylim_Temp<-c(-1,4)
col_Temp<-"red3"
lty_Temp<-1
lwd_Temp<-1
Ylab_Temp<-expression(paste('Temperature (',degree,'C)'))

Ylim_Food<-c(0,1600)
col_Food<-"blue"
lty_Food<-8
lwd_Food<-1
Ylab_Food<-expression(paste('Available food (mg.C.m'^-3,')'))

Ylim_DL<-c(0,24)
col_DL<-"black"
lty_DL<-3
lwd_DL<-1
Ylab_DL<-"Day Length (Hours)"

plot(xTemp, yTemp, axes=F, ylim=Ylim_Temp, xlab='', ylab='', type='l', col=col_Temp, lty=lty_Temp,main='', xlim=Xlim, lwd=lwd_Temp)
axis(2, ylim=Ylim_Temp,col=col_Temp,lwd=1,col.axis=col_Temp)
mtext(2,text=Ylab_Temp,line=2,col=col_Temp, cex=0.75)

par(new=T)
plot(xFood, yFood, axes=F, ylim=Ylim_Food, xlab='', ylab='', type='l', col=col_Food, lty=lty_Food, main='', xlim=Xlim, lwd=lwd_Food)
axis(2, ylim=Ylim_Food,lwd=1,line=3.5, col=col_Food,col.axis=col_Food)
mtext(2,text=Ylab_Food,line=5.5, col=col_Food, cex=0.75)

par(new=T)
plot(xDayLength, yDayLength, axes=F, ylim=Ylim_DL, xlab='', ylab='', type='l', col=col_DL, lty=lty_DL, main='',xlim=Xlim,lwd=lwd_DL)
axis(2, ylim=Ylim_DL,lwd=1,line=7, col=col_DL,col.axis=col_DL)
mtext(2,text=Ylab_DL,line=9, col=col_DL, cex=0.75)

# plot tick marks for IMP
par(new=T)
plot(NA, NA, axes=F, ylim=Ylim_IMP, xlab='', ylab='', main='', xlim=Xlim_IMP)
for (i in 1:length(xIMP)) lines(rep(xIMP[i],2),yIMP[i,],col=col_IMP[i],lwd=lwd_IMP)

#We can now draw the X-axis, which is of course shared by all the three time-series.

axis(1,pretty(range(0,1),10))
mtext(Xlab,side=1,col='black',line=2, cex=0.75)

# return plotting to terminal

if(PLOT.TIF) dev.off()

############# End printing to TIF file



```
