Krill EMC Results - under conditions of intra-specific competition

========================================================

The scenarios presented here relate to conditions of limiting resources.  
Limitation is by the volume of new water filtered relative to the maximum filtration rate.  If consumption competition applies then the ratio of water filtered to maximum filtration is governed by population size.  If competition is governed by body size e.g. larger bodies have an advantage through displacement or smaller bodies have an advantage through agility, then filration rate will be adjusted accordingly.

These scenarios do not reflect population size or structure except in a relative sense to illustrate the consequences of limiting resources and different forms of intraspecific competition.


```{r}
# 0. Set up directories, functions, libraries and initial parameters for test

# 0.1 ancillary directories

dir_fns<-"Fns\\"
dir_data<-"Data\\"
dir_out<-"Out\\"

# 0.2 load functions 

# old source(paste(dir_fns,"Growth_Fn_EMC.r",sep=""))

source(paste(dir_fns,"Growth_Fn_EMC_v2.r",sep=""))

# 0.3 load libraries

library(plotrix)
library(R2HTML)

# 0.4. initialise parameters (EMC_p)

source(paste(dir_data,"Growth_data_KrillParams.r",sep=""))

# 0.5. Area-specific environment (AreaEnv) and other local variables

source(paste(dir_data,"Growth_data_Env.r",sep=""))

```

# 1. Initialise conditions for parsing to the function and name according to function variables

```{r}
# 1.1 Initialise trial

ActiveArea<-20  # which area is to be used
                # note that this will be made into a relative abundance of food

Start_asPropYr <- 0  # 1 January
Gstate<-list(iG     = 0 # investment in growth within moult
            ,IMP    = 0 # where IMP is prop of IMP completed
            ,IMPtime = 0 # time in IMP so far (years)
            ,DayLength_LastMoult = DL_EMC(Area_lat[Area_n==ActiveArea],Start_asPropYr)  # day length at last moult
            )

Rstate<-list(iR     = 0 #   Ir is investment in reproduction within moult cycle
           , Moults = 0 # how many moults have passed in stage of cycle
           , Cycle  = 3 # which stage of the cycle is currently active  - note that this is set for any age
           )

Carbon<-list(Cingest = 0
            ,Cassim  = 0
            ,Cegest  = 0
            ,Cexcess = 0
            ,BodyCarbon = NA
            )
Local<-list(AreaLat = Area_lat[Area_n==ActiveArea]  # latitude of location to give day length
            , Env = AreaEnv[(AreaEnv[,1]==ActiveArea),c(3:ncol(AreaEnv))]
            )

Local$Env[,3]<-1.5E3  #  value at maximum production for 30 mm, -1oC, female


print(Local$Env)
```




```{r}
# Set specific conditions for trial

Start.Age<-1
Start.Length<-20   
Start.WhichSex<-2   # 1 = male, 2 = female, 3 = mature female
Start.StartProj<-0  # project for one year
Start.EndProj<-1


# Filtering Efficiency is used to scale the food in the area to available food per volume for an individual


Filt_Eff<- 0.06  # set this to determine how much of the food is available in the volume being filtered (accounts for competition)



ResMoults<-NULL
IntSex <-c(1,2)
IntLen <-c(30,40,50,60)
IntTemp <- (c(-10:50)/10)
IntFilt_Eff <- c(0.05,0.5,1) 
  
for (s in IntSex){
  for (Length in IntLen){
    for (Temp in IntTemp){
      Local$Env[,2]<-Temp

      for (Filt_Eff in IntFilt_Eff){
    
Run.WhichSex<- s

Age    <- 3
DryWeight<-DW_from_Length(Length,EMC_p$LW,Run.WhichSex)
Kstate<-list(Gro=Gstate, Rep = Rstate, Carbon = Carbon, Female= (if(Run.WhichSex==1) FALSE else TRUE))
Kstate$Carbon$BodyCarbon<-CW_from_Length(Length,EMC_p$LW,2)
StartProj<-Start.StartProj  # project for one year
EndProj<-Start.EndProj

Total_proj<-NULL

res<-Growth_EMC(Age      
          ,Length     
          ,DryWeight
          ,Kstate
          ,Filt_Eff
          ,StartProj   
          ,EndProj     
          ,Local       
          ,EMC_p       
          )
ResMat<-matrix(res$Moults$Data,ncol=res$Moults$Vars,byrow=res$Moults$ByRow)
RMrows<-nrow(ResMat)
ResMoults<-rbind(ResMoults,
                 c(s,Length,Temp,Filt_Eff, # treatments at beginning
                   Age,DryWeight,     # initial age and dryweight
                   ResMat[RMrows,10], # final length
                   ResMat[RMrows,11], # final dryweight
                   sum(ResMat[,15]))  # total eggs
                   ) # end rbind

} # end Length
} # end Temp
} # end Filt_Eff
} # end sex



# Results for each moult are in res$Moults
 
dimnames(ResMoults)[[2]]= c( "Sex"
                            ,"Length"
                            ,"Temp"
                            ,"Filt_Eff"
                            ,"Age"
                            ,"DW_init"
                            ,"Len_end"
                            ,"DW_end"
                            ,"Eggs_total"
                             ) # end names

print(ResMoults)
```

## Plots


```{r echo=FALSE}


PlotVar<-function(VX,  # variable on X axis
                  VY,  # variable on Y axis
                  VYdenom, # divide VY by this quantity, make = VY if not to use a variable in Res
                  ML,  # variable for multiple lines
                  PV1, # panel variable 1 # rows
                  PV2, # panel variable 2 # columns
                  Res,  # results matrix
                  LimX, # limits to X axis (if NULL then work them out)
                  LimY,  # limits to Y axis (if NULL then work out)
                  colML, # colours for multiple lines
                  ltyML, # line types for multiple lines
                  Row_Yaxis_Var,
                  Vary_Yaxis_row,
                  LabX, # label for X axis
                  LabY,  # label for Y axis
                  NamePV1,
                  NamePV2,
                  setPanelPlots, # if wish to do a panel of plots rows = PV1 and cols = PV2
                  TMT_rows_text,
                  TMT_rows_text_line,
                  TMT_cols_text,
                  TMT_cols_text_line,
                  vOMA,
                  PLOT.TIF,
                  TIF.Filename,
                  TIF.dim # e.g. list (height = 6, width = 8.5, units = 'cm', res = 1500)
                  ){

  # if plotting for publication - advice here https://danieljhocking.wordpress.com/2013/03/12/high-resolution-figures-in-r/
  #   tiff("FileName.tiff", height = 12, width = 17, units = 'cm', compression = "lzw", res = 300)
  
 if(PLOT.TIF) tiff(filename = TIF.Filename, height = TIF.dim$height, width = TIF.dim$width
                                          , units = TIF.dim$units, res = TIF.dim$res)


 if(VYdenom != VY) Res[,VY]<-Res[,VY]/Res[,VYdenom]  # standardises quantity to initial quantity if needed e.g. length, dry weight
 
 
 vals_PV1<-unique(Res[,PV1])
 vals_PV2<-unique(Res[,PV2])
 
 # set panel of plots
 if(setPanelPlots) {
   op<-par(no.readonly = TRUE) # saving par in order to restore it at end
   if (!is.null(vOMA)) par(oma=vOMA + 0.1)
   par(mfrow=c(length(vals_PV1),length(vals_PV2)))
   par(mar=c(1.0,0.75,0.5,0.5)) 
 }
 
 vals_ML <-unique(Res[,ML])
 if (is.null(LimX)) LimX <- c(min(Res[,VX]),max(Res[,VX]))
 if (is.null(LimY)) LimY <- c(min(Res[,VY]),max(Res[,VY]))
 if (is.null(colML)) colML <- c(1:length(vals_ML))
 if (is.null(ltyML)) ltyML <- c(1:length(vals_ML))
 
 for (i in 1:length(vals_PV1)){
   labelX <- LabX
   if(Vary_Yaxis_row) {LimY<-Row_Yaxis_Var[[i]]$LimY; nYticks<-Row_Yaxis_Var[[i]]$nYticks; at_tickY<-Row_Yaxis_Var[[i]]$at_tickY} else
                      {nYticks<-NULL; at_tickY<-NULL}
     
     labelTickX<- TRUE
     labelTickY<- TRUE

   if (setPanelPlots){ 
     labelX<- ""
     if (i!=length(vals_PV1)) labelTickX<- FALSE else TRUE
      }
   for (j in 1:length(vals_PV2)){
     pd<-Res[Res[,PV1]==vals_PV1[i] & Res[,PV2]==vals_PV2[j],c(VX,VY,ML)]

     labelY <- LabY
    if (setPanelPlots){ 
      labelY<- ""
      if (j!=1) labelTickY<-  FALSE else TRUE 
      }
     PlotTitle <-if (!setPanelPlots) paste(NamePV1," ",vals_PV1[i]," : ",NamePV2," ",vals_PV2[j],sep="") else ""
     plot(NA,NA,xlim=LimX,ylim=LimY, xlab=labelX,ylab=labelY,main=PlotTitle, xaxt="n",yaxt="n",lwd=1,bty="n")
     box(lwd=1)
     axis(side=1,labels=labelTickX, at=c(-1,0,1,2,3,4,5),lwd=1, cex.axis=0.75)
     axis(side=2,labels=labelTickY, at=at_tickY,lwd=1, cex.axis=0.75)
     
     for (m in 1:length(vals_ML)) lines(pd[pd[,3]==vals_ML[m],1],pd[pd[,3]==vals_ML[m],2],col=colML[m],lty=ltyML[m],lwd=1)

   } # end j
 } # end i
  
 if(setPanelPlots) { # add annotations
      mtext(side=2,text=LabY, line=2, col="black",cex=0.75,outer=TRUE)
      mtext(side=3,text=TMT_cols_text, line=TMT_cols_text_line, col="black",cex=0.75,outer=TRUE,font=4)
      mtext(side=1,text=expression(paste('Temperature (',degree,'C)')), line=1.5, col="black",cex=0.75,outer=TRUE)
      mtext(side=2,text=TMT_rows_text, line=TMT_rows_text_line, col="black",cex=0.75,outer=TRUE,font=4)
   
      par(op) # restore par

       }

 if(PLOT.TIF) dev.off()

 } # end PlotVar

```

Variables
1 "Sex"
2 "Length"
3 "Temp"
4 "Filt_Eff"
5 "Age"
6 "DW_init"
7 "Len_end"
8 "DW_end"
9 "Eggs_total"


## Length

```{r echo=FALSE}
# subset data
RMd<-ResMoults

TMT_rows_text<-"     1.0 Food               0.5 Food           0.05 Food"              ###########
TMT_rows_text_line<-4
TMT_cols_text<-'   Males                                                                     Females'  ######### end of line
TMT_cols_text_line<-1
vOMA<-c(4, 5.5, 3, 1)


Row_Yaxis_Var<-list(r1 = list(LimY=c(0  ,1.1), nYticks=6, at_tickY=c(0,0.2,0.4,0.6,0.8,1.0)),
                    r2 = list(LimY=c(0.9,1.6), nYticks=4, at_tickY=c(1.0,1.2,1.4,1.6)),
                    r3 = list(LimY=c(0.9,2.5), nYticks=4, at_tickY=c(1.0,1.5,2.0,2.5)))

print(Row_Yaxis_Var)

  PlotVar(3,  # variable on X axis
        7,  # variable on Y axis
        2,  # denominator to divide into VY.  same as VY if not required
        2,  # variable for multiple lines
        4, # panel variable 1  - rows
        1, # panel variable 2  - columns
        RMd,  # results matrix
        NULL, # limits to X axis (if NULL then work them out)
        NULL,  # limits to Y axis (if NULL then work out)
        NULL, # colours for multiple lines
        NULL, # line types for multiple lines
        Row_Yaxis_Var,
        TRUE, #Vary_Yaxis_row = 
        expression(paste('Temperature (',degree,'C)')), # label for X axis
        "Proportion initial Length",  # label for Y axis
        "Fe",
        "Sex",
        TRUE, # if wish to do a panel of plots rows = PV1 and cols = PV2
        TMT_rows_text,
        TMT_rows_text_line,
        TMT_cols_text,
        TMT_cols_text_line,
        vOMA,
        TRUE, # PLOT.TIF,
        'EMC_food_sex_size.tif',#          TIF.Filename
        list (height = 100, width = 170, units = 'mm', res = 300) # TIF.dim
         )# end call to PlotVar

```

if(PLOT.TIF) tiff(filename = "EMC_old_growth_models v3.tif", width = 170, height = 100, units = "mm", res=300)



## Eggs

```{r echo=FALSE}

# subset data
RMd<-ResMoults[(ResMoults[,1]==2 & ResMoults[,4]>0.1),]
RMd[,9]<-RMd[,9]/1000  # total number of eggs as 1000's
TMT_rows_text<-'       1.0 Food                      0.5 Food'
TMT_rows_text_line<-3.5
TMT_cols_text<-'Females'
TMT_cols_text_line<-1
vOMA<-c(3, 10, 3, 10)

Row_Yaxis_Var<-list(r1 = list(LimY=c(0  ,5), nYticks=6, at_tickY=c(0,1,2,3,4,5)),
                    r2 = list(LimY=c(10 ,50), nYticks=5, at_tickY=c(10,20,30,40,50)))


PlotVar(3,  # variable on X axis
        9,  # variable on Y axis
        9,  # denominator to divide into VY.  same as VY if not required
        2,  # variable for multiple lines
        4, # panel variable 1  - rows
        1, # panel variable 2  - columns
        RMd,  # results matrix
        NULL, # limits to X axis (if NULL then work them out)
        NULL,  # limits to Y axis (if NULL then work out)
        NULL, # colours for multiple lines
        NULL, # line types for multiple lines
        Row_Yaxis_Var,
        TRUE, # Vary_Yaxis_row = 
        expression(paste('Temperature (',degree,'C)')), # label for X axis
        "Total Eggs (,000)",  # label for Y axis
        "Fe",
        "Sex",
        TRUE, # if wish to do a panel of plots rows = PV1 and cols = PV2
        TMT_rows_text,
        TMT_rows_text_line,
        TMT_cols_text,
        TMT_cols_text_line,
        vOMA,
        TRUE, # PLOT.TIF,
        'EMC_food_sex_eggs.tif', #          TIF.Filename
        list (height = 100, width = 170, units = 'mm', res = 300) # TIF.dim
         )# end call to PlotVar

```
